### 2017-11-23 UOW_thesis_template_v2-0/thesis_template/chapters/jumpdiffAmer.tex
:art: Jeff's changes before Marianito's help

    and at $x = S^*(t)$, the following smooth pasting conditions are satisfied:

@@

        \fr{\pr \tilde{ v}_{\text{a}}^{\text{put}}}{\pr t}(\xi,t) - \left(p_\lambda(\xi) - \lambda\E[Y^{-\xi}]\right)\tilde{ v}_{\text{a}}^{\text{put}}(\xi,t) = \tilde{g}(\xi,t).

@@

        	\subsection{Example: lognormally distributed jumps for an American put option}
        	As a special case for the American put option, we will assume that the underlying asset follows lognormally distributed jump dynamics. This will allow us to evaluate a few of the integrals that appear in~\eqref{eqn:amerJumpPut}. As a preparatory step, we will first denote the triple integral in~\eqref{eqn:amerJumpPut} by $I$. Then using the expression for $g_p$ from~\eqref{eqn:g}, we see that
        	\begin{align*}
        		I &= -rK \int_t^T\int_0^\infty\int_0^{S^*(u)}\fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad + q \int_t^T\int_0^\infty\int_0^{S^*(u)}\fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad + \int_t^T\int_0^\infty\int_0^{S^*(u)} \fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{z}{w},t,u \right) \\
        		&{} \quad \quad \times  \lambda \int_{S^*(u)/z}^\infty \left( v_{\text{a}}^{\text{put}}(zy,t) - (K-zy) \right)f(y) \, \d y \, \d z \, \d w \, \d u \\
        		& = I_1 + I_2 + I_3,
        	\end{align*}
        	where we had to swap the integrals with respect to $w$ and $z$ in order to simplify the Heaviside function that appears in $g_p$. Each of these integrals will be investigated separately to see if they can be simplified. For $I_1$, we will make use of eq.~\eqref{eqn:jump11} for $\J$ and the first identity in~\eqref{eqn:shiftKernel} for $\K_\lambda$ (assuming time-constant functions for $r$, $q$, and $\sigma$) to get
        		\begin{align*}
        			I_1 &= -rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \int_0^\infty\int_0^{S^*(u)} \fr{1}{w} \delta(w-1) \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			& {}\quad -rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!\sqrt{n\sigma_Y^2}}\int_0^\infty \int_0^{S^*(u)} \fr{1}{zw}N'\left( \fr{\log w + n\mu_Y}{\sqrt{n\sigma_Y^2}} \right) \\
        			& {} \quad \quad \times N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			&= I_{1,a} + I_{1,b}.
        		\end{align*}
		For $I_{1,a}$, we swap the order of integration between $z$ and $w$ (constant limits with respect to each of these dummy variables) and using the well known result of $f(a) = \int_0^\infty \delta(x-a) f(x) \, \d x$ for $a > 0$ to obtain
        		$$
        			I_{1,a} = -rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}}\int_0^{S^*(u)} \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{z}, t, u \right) \right) \, \d z \, \d u.
        		$$
		Then we employ Lemma~\ref{lem:2a} and referring to~\eqref{eqn:z2lambda} for the complete expression of $z_{2\lambda}$, we can assign
			$$
				a = 0, \enskip b = S^*(u), \enskip a_1 = \fr{1}{\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}, \enskip
			b_1 = z_2\left( \fr{x}{z}, t, u \right),
			$$
		which then gives us
			\begin{align*}
				I_{1,a} &=  -rK\int_t^T e^{(r+\lambda)(u-t)}N\left(-z_{2\lambda}\left( \fr{x}{S^*(u)},t,u\right) \right) \, \d u.
			\end{align*}
			Unfortunately, the time integral cannot be solved analytically without prior knowledge of $S^*$ so it will be left unsimplified

        	For $I_{1,b}$, we once again swap the order of integration between $z$ and $w$. Then we make use of lemma~\ref{lem:1} because $z_{2\lambda}$ takes the form of a logarithmic function. In accordance to Lemma~\ref{lem:1}, we make the following declarations
        		$$
        			a_1 = \fr{1}{\sqrt{n\sigma_Y^2}}, \enskip b_1 = \fr{n\mu_Y}{\sqrt{n\sigma_Y^2}}, \enskip
        			a_2 = \fr{1}{\sigma\sqrt{u-t}}, \enskip b_2 = z_{2\lambda}\left( \fr{x}{z}, t, u\right),
        		$$
	and integrating with respect to $w$ leaves us with
			\begin{align*}
				I_{1,b} &= -rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}  e^{(r+\lambda)(u-t)} \int_0^{S^*(u)} \fr{1}{z}  N\left(Z_n \left( \fr{x}{z},t,u  \right) \right) \,\d z \, \d u,
			\end{align*}
	where $Z_n$ is defined in~\eqref{eqn:zn}. To compute the integral with respect to $z$, we once again incorporate lemma~\ref{lem:2a} and set 
		$$
			a = 0, \enskip b = S^*(u), \enskip a_1 = \fr{1}{\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}, \enskip
			b_1 = Z_n\left( \fr{x}{z}, t, u \right),
		$$
		to obtain
		$$
			I_{1,b} = -rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!}  e^{(r+\lambda)(u-t)} N\left(- Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u.
		$$
		Now adding $I_{1,a}$ and $I_{1,b}$ gives us the original integral $I_1$, and finally
		\begin{align}
			I_1 &= -rK\int_t^T e^{(r+\lambda)(u-t)}N\left(-z_{2\lambda}\left( \fr{x}{S^*(u)},t,u\right) \right) \, \d u \nonumber \\
			 &\quad -rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!}  e^{(r+\lambda)(u-t)} N\left(- Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u \nonumber \\
			 &= -rK \ds\sum\limits_{n=0}^{\infty}\int_t^T  \fr{(\lambda(u-t))^n}{n!} e^{(r+\lambda)(u-t)} N\left(-Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u, \label{eqn:I1put}
		\end{align}
		where after comparing $z_{2\lambda}$ and $Z_n$ (i.e., when $n=0$, $Z_0 = z_{2\lambda}$), the summation can actually encompass both terms with an extended summation index to $n=0$. This was not possible to do before as the original summation term that appears in $\J$ possessed a fraction that would have been undefined at $n=0$.

@@

		with $z_{1\lambda}$ from~\eqref{eqn:z1lambda}. Similarly for $I_{2,b}$, we apply the same procedure as we did for $I_{1,b}$ except when using lemma~\ref{lem:1}, we choose

@@

	To compute the remaining integral with respect to $z$, we once again have the aid of the second result from lemma~\ref{lem:2a} and set

@@

		The innermost integral can be evaluated using lemma~\ref{lem:2b} and the associated variables be set to

@@

		The innermost integral with respect to $w$ is computed first with the help of lemma~\ref{lem:2a} by choosing

@@

		Similar to how we handled $I_{3,a}$, we interchange the order of integration between $y$ and $z$, declare a substitution of $p = (zy)/S^*(u)$, then reverse the integration between $p$ and $y$. The result of these steps is

@@

		where we also replaced $f$ with the PDF for a lognormal distribution. The integral with respect to $y$ can be integrated by lemma~\ref{lem:2b} with

@@

        	First, we let the triple integral in~\eqref{eqn:amerJumpPut} be $I$. Then using the expression for $g_c$ from~\eqref{eqn:g} gives
        	\begin{align*}
        		I &= rK \int_t^T\int_0^\infty\int_{S^*(u)}^\infty\fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad - q \int_t^T\int_0^\infty\int_{S^*(u)}^\infty\fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad + \int_t^T\int_0^\infty\int_{S^*(u)}^\infty \fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{z}{w},t,u \right) \\
        		&{} \quad \quad \times  \lambda \int_{0}^{S^*(u)/z} \left( v_{\text{a}}^{\text{call}}(zy,t) - (zy-K) \right)f(y) \, \d y \, \d z \, \d w \, \d u \\
        		& = I_1 + I_2 + I_3,
        	\end{align*}
        	where the order of integration between $z$ and $w$ had to be swapped in order to simplify the Heaviside function in $g_c$. We first look at $I_1$ and incorporate eq.~\eqref{eqn:jump11} for $\J$ and the first identity for $\K_\lambda$ in~\eqref{eqn:shiftKernel} to arrive at
        	        		\begin{align*}
        			I_1 &= rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \int_0^\infty\int_{S^*(u)}^\infty \fr{1}{w} \delta(w-1) \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			& {}\quad rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!\sqrt{n\sigma_Y^2}}\int_0^\infty \int_{S^*(u)}^\infty \fr{1}{zw}N'\left( \fr{\log w + n\mu_Y}{\sqrt{n\sigma_Y^2}} \right) \\
        			& {} \quad \quad \times N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			&= I_{1,a} + I_{1,b},
        		\end{align*}
        		where we assumed $r$, $q$, and $\sigma$ are constants. Now for $I_{1,a}$, the limits of integration for $z$ and $w$ are constants with respect to each other. So we will swap them and then use $f(a) = \int_0^\infty \delta(x-a) f(x) \, \d x$ for $a > 0$ to obtain
        		$$
        			I_{1,a} = rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}}\int_{S^*(u)}^\infty \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{z}, t, u \right) \right) \, \d z \, \d u.
        		$$
		Making use of lemma~\ref{lem:2a} and checking the full form of $z_{2\lambda}$ in~\eqref{eqn:z2lambda} allows us to set
			$$
				a = S^*(u), \enskip b = \infty, \enskip a_1 = \fr{1}{\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}, \enskip
			b_1 = z_2\left( \fr{x}{z}, t, u \right),
			$$
		to give
			\begin{align*}
				I_{1,a} &=  rK\int_t^T e^{(r+\lambda)(u-t)}N\left(z_{2\lambda}\left( \fr{x}{S^*(u)},t,u\right) \right) \, \d u.
			\end{align*}
		We cannot proceed to simplify this as the integral with respect to $u$ cannot be computed without knowing $S^*$ for all of $u$ from $t$ to $T$.

        	The integral $I_{1,b}$ is treated in a similar manner. We once again swap the order of integration between $z$ and $w$. Then lemma~\ref{lem:1} will be used since $z_{2\lambda}$ is actually a logarithmic function. To utilize lemma~\ref{lem:1}, we need to set
        		$$
        			a_1 = \fr{1}{\sqrt{n\sigma_Y^2}}, \enskip b_1 = \fr{n\mu_Y}{\sqrt{n\sigma_Y^2}}, \enskip
        			a_2 = \fr{1}{\sigma\sqrt{u-t}}, \enskip b_2 = z_{2\lambda}\left( \fr{x}{z}, t, u\right),
        		$$
	and integrating with respect to $w$ leaves us with
			\begin{align*}
				I_{1,b} &= rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}  e^{(r+\lambda)(u-t)} \int_{S^*(u)}^\infty \fr{1}{z}  N\left(Z_n \left( \fr{x}{z},t,u  \right) \right) \,\d z \, \d u,
			\end{align*}
	with $Z_n$ defined in~\eqref{eqn:zn}. We once again incorporate lemma~\ref{lem:2a} to complete the integral in $z$ by setting 
		$$
			a = S^*(u), \enskip b = \infty, \enskip a_1 = \fr{1}{\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}, \enskip
			b_1 = Z_n\left( \fr{x}{z}, t, u \right),
		$$
		to obtain
		$$
			I_{1,b} = rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!}  e^{(r+\lambda)(u-t)} N\left(Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u.
		$$
		Now that all the simplifications have been performed, we now recover $I_1$ by adding $I_{1,a}$ and $I_{1,b}$ to get
		\begin{align}
			I_1 &= rK\int_t^T e^{(r+\lambda)(u-t)}N\left(z_{2\lambda}\left( \fr{x}{S^*(u)},t,u\right) \right) \, \d u \nonumber \\
			 &\quad rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!}  e^{(r+\lambda)(u-t)} N\left(Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u \nonumber \\
			 &= rK \ds\sum\limits_{n=0}^{\infty}\int_t^T  \fr{(\lambda(u-t))^n}{n!} e^{(r+\lambda)(u-t)} N\left(Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u, \label{eqn:I1call}
		\end{align}
		where the summation can be extended to $n=0$ when we see that $z_{2\lambda} = Z_n$ for $n=0$. Like the American put, we could not immediately make this observation since $\J$ had a fraction where $n=0$ would render it undefined.

		The integral $I_2$ follows a similar path for the lemmas and techniques used in deriving the analogous term with the American put. The lengthy calculations will be omitted, but the result is
        	\begin{equation}
        		\label{eqn:I2put}
        		I_2 = qx  \ds\sum\limits_{n=0}^{\infty}\int_t^T   \fr{(\lambda(u-t))^n}{n!} e^{n\mu_Y + n\sigma_Y^2/2} e^{(q+\lambda + \kappa\lambda)(u-t)} N\left( D_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u,
        	\end{equation}
	with $D_n$ defined in~\eqref{eqn:Dn}. 
	However, we will be providing the complete derivation and solution of $I_3$ as this term is mildly involved. As we will see, the result of $I_3$ will be a double integral which is more ideal to work with in comparison to a quadruple integral.

>>>>

    and at $x = S^*(t)$, the following smooth pasting conditions are assumed to be satisfied:

@@

        \fr{\pr \tilde{ v}_{\text{a}}^{\text{put}}}{\pr t}(\xi,t) - \left(p_\lambda(\xi) - \lambda\E[Y^{-\xi}]\right)\tilde{ v}_{\text{a}}^{\text{put}}(\xi,t) = \tilde{g}(\xi,t),

@@

        	\subsection{Example: lognormally distributed jumps for an American put option}
        	As a special case for the American put option, we will assume that the underlying asset follows lognormally distributed jump dynamics. This will allow us to evaluate a few of the integrals that appear in~\eqref{eqn:amerJumpPut}. As a preparatory step, we will first denote the triple integral in~\eqref{eqn:amerJumpPut} by $I$. Then using the expression for $g_p$ from~\eqref{eqn:g}, we see that
        	\begin{align*}
        		I &= -rK \int_t^T\int_0^\infty\int_0^{S^*(u)}\fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad + q \int_t^T\int_0^\infty\int_0^{S^*(u)}\fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad + \int_t^T\int_0^\infty\int_0^{S^*(u)} \fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{z}{w},t,u \right) \\
        		&{} \quad \quad \times  \lambda \int_{S^*(u)/z}^\infty \left( v_{\text{a}}^{\text{put}}(zy,t) - (K-zy) \right)f(y) \, \d y \, \d z \, \d w \, \d u \\
        		& = I_1 + I_2 + I_3,
        	\end{align*}
        	where we had to swap the integrals with respect to $w$ and $z$ in order to simplify the Heaviside function that appears in $g_p$. Each of these integrals will be investigated separately to see if they can be simplified. For $I_1$, we will make use of Eq.~\eqref{eqn:jump11} for $\J$ and the first identity in~\eqref{eqn:shiftKernel} for $\K_\lambda$ (assuming time-constant functions for $r$, $q$, and $\sigma$) to get
        		\begin{align*}
        			I_1 &= -rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \int_0^\infty\int_0^{S^*(u)} \fr{1}{w} \delta(w-1) \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			& {}\quad -rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!\sqrt{n\sigma_Y^2}}\int_0^\infty \int_0^{S^*(u)} \fr{1}{zw}N'\left( \fr{\log w + n\mu_Y}{\sqrt{n\sigma_Y^2}} \right) \\
        			& {} \quad \quad \times N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			&= I_{1,a} + I_{1,b}.
        		\end{align*}
		For $I_{1,a}$, we swap the order of integration between $z$ and $w$ (constant limits with respect to each of these dummy variables) and using the well known result of $f(a) = \int_0^\infty \delta(x-a) f(x) \, \d x$ for $a > 0$ to obtain
        		$$
        			I_{1,a} = -rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}}\int_0^{S^*(u)} \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{z}, t, u \right) \right) \, \d z \, \d u.
        		$$
		Then we employ Lemma~\ref{lem:2a} and referring to~\eqref{eqn:z2lambda} for the complete expression of $z_{2\lambda}$, we can assign
			$$
				a = 0, \enskip b = S^*(u), \enskip a_1 = \fr{1}{\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}, \enskip
			b_1 = z_2\left( \fr{x}{z}, t, u \right),
			$$
		which then gives us
			\begin{align*}
				I_{1,a} &=  -rK\int_t^T e^{(r+\lambda)(u-t)}N\left(-z_{2\lambda}\left( \fr{x}{S^*(u)},t,u\right) \right) \, \d u.
			\end{align*}
			Unfortunately, the time integral cannot be solved analytically without prior knowledge of $S^*$ so it will be left unsimplified

        	For $I_{1,b}$, we once again swap the order of integration between $z$ and $w$. Then we make use of Lemma~\ref{lem:1} because $z_{2\lambda}$ takes the form of a logarithmic function. In accordance to Lemma~\ref{lem:1}, we make the following declarations
        		$$
        			a_1 = \fr{1}{\sqrt{n\sigma_Y^2}}, \enskip b_1 = \fr{n\mu_Y}{\sqrt{n\sigma_Y^2}}, \enskip
        			a_2 = \fr{1}{\sigma\sqrt{u-t}}, \enskip b_2 = z_{2\lambda}\left( \fr{x}{z}, t, u\right),
        		$$
	and integrating with respect to $w$ leaves us with
			\begin{align*}
				I_{1,b} &= -rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}  e^{(r+\lambda)(u-t)} \int_0^{S^*(u)} \fr{1}{z}  N\left(Z_n \left( \fr{x}{z},t,u  \right) \right) \,\d z \, \d u,
			\end{align*}
	where $Z_n$ is defined in~\eqref{eqn:zn}. To compute the integral with respect to $z$, we once again incorporate Lemma~\ref{lem:2a} and set 
		$$
			a = 0, \enskip b = S^*(u), \enskip a_1 = \fr{1}{\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}, \enskip
			b_1 = Z_n\left( \fr{x}{z}, t, u \right),
		$$
		to obtain
		$$
			I_{1,b} = -rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!}  e^{(r+\lambda)(u-t)} N\left(- Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u.
		$$
		Now adding $I_{1,a}$ and $I_{1,b}$ gives us the original integral $I_1$, and finally
		\begin{align}
			I_1 &= -rK\int_t^T e^{(r+\lambda)(u-t)}N\left(-z_{2\lambda}\left( \fr{x}{S^*(u)},t,u\right) \right) \, \d u \nonumber \\
			 &\quad -rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!}  e^{(r+\lambda)(u-t)} N\left(- Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u \nonumber \\
			 &= -rK \ds\sum\limits_{n=0}^{\infty}\int_t^T  \fr{(\lambda(u-t))^n}{n!} e^{(r+\lambda)(u-t)} N\left(-Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u, \label{eqn:I1put}
		\end{align}
		where after comparing $z_{2\lambda}$ and $Z_n$ (i.e., when $n=0$, $Z_0 = z_{2\lambda}$), the summation can actually encompass both terms with an extended summation index to $n=0$. This was not possible to do before as the original summation term that appears in $\J$ possessed a fraction that would have been undefined at $n=0$.

@@

		with $z_{1\lambda}$ from~\eqref{eqn:z1lambda}. Similarly for $I_{2,b}$, we apply the same procedure as we did for $I_{1,b}$ except when using Lemma~\ref{lem:1}, we choose

@@

	To compute the remaining integral with respect to $z$, we once again have the aid of the second result from Lemma~\ref{lem:2a} and set

@@

		The innermost integral can be evaluated using Lemma~\ref{lem:2b} and the associated variables be set to

@@

		The innermost integral with respect to $w$ is computed first with the help of Lemma~\ref{lem:2a} by choosing

@@

		Similar to how we dealt with $I_{3,a}$, we interchange the order of integration between $y$ and $z$, declare a substitution of $p = (zy)/S^*(u)$, then reverse the integration between $p$ and $y$. The result of these steps is

@@

		where we also replaced $f$ with the PDF for a lognormal distribution. The integral with respect to $y$ can be integrated by Lemma~\ref{lem:2b} with

@@

        	First, we let the triple integral in~\eqref{eqn:amerJumpPut} be $I$. Then using the expression for $g_c$ from~\eqref{eqn:g} gives
        	\begin{align*}
        		I &= rK \int_t^T\int_0^\infty\int_{S^*(u)}^\infty\fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad - q \int_t^T\int_0^\infty\int_{S^*(u)}^\infty\fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{x}{zw},t,u \right) \, \d z \, \d w \, \d u \\
        		& {} \quad + \int_t^T\int_0^\infty\int_{S^*(u)}^\infty \fr{1}{w}\J(w,t,u)\fr{1}{z}\K_\lambda\left( \fr{z}{w},t,u \right) \\
        		&{} \quad \quad \times  \lambda \int_{0}^{S^*(u)/z} \left( v_{\text{a}}^{\text{call}}(zy,t) - (zy-K) \right)f(y) \, \d y \, \d z \, \d w \, \d u \\
        		& = I_1 + I_2 + I_3,
        	\end{align*}
        	where the order of integration between $z$ and $w$ had to be swapped in order to simplify the Heaviside function in $g_c$. We first look at $I_1$ and incorporate eq.~\eqref{eqn:jump11} for $\J$ and the first identity for $\K_\lambda$ in~\eqref{eqn:shiftKernel} to arrive at
        	        		\begin{align*}
        			I_1 &= rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \int_0^\infty\int_{S^*(u)}^\infty \fr{1}{w} \delta(w-1) \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			& {}\quad rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}} \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!\sqrt{n\sigma_Y^2}}\int_0^\infty \int_{S^*(u)}^\infty \fr{1}{zw}N'\left( \fr{\log w + n\mu_Y}{\sqrt{n\sigma_Y^2}} \right) \\
        			& {} \quad \quad \times N'\left( z_{2\lambda}\left( \fr{x}{zw}, t, u \right) \right) \, \d z \, \d w \, \d u \\
        			&= I_{1,a} + I_{1,b},
        		\end{align*}
        		where we assumed $r$, $q$, and $\sigma$ are constants. Now for $I_{1,a}$, the limits of integration for $z$ and $w$ are constants with respect to each other. So we will swap them and then use $f(a) = \int_0^\infty \delta(x-a) f(x) \, \d x$ for $a > 0$ to obtain
        		$$
        			I_{1,a} = rK\int_t^T \fr{e^{(r+\lambda)(u-t)}}{\sigma\sqrt{u-t}}\int_{S^*(u)}^\infty \fr{1}{z} N'\left( z_{2\lambda}\left( \fr{x}{z}, t, u \right) \right) \, \d z \, \d u.
        		$$
		Making use of Lemma~\ref{lem:2a} and checking the full form of $z_{2\lambda}$ in~\eqref{eqn:z2lambda} allows us to set
			$$
				a = S^*(u), \enskip b = \infty, \enskip a_1 = \fr{1}{\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}, \enskip
			b_1 = z_2\left( \fr{x}{z}, t, u \right),
			$$
		to give
			\begin{align*}
				I_{1,a} &=  rK\int_t^T e^{(r+\lambda)(u-t)}N\left(z_{2\lambda}\left( \fr{x}{S^*(u)},t,u\right) \right) \, \d u.
			\end{align*}
		We cannot proceed to simplify this as the integral with respect to $u$ cannot be computed without knowing $S^*$ for all of $u$ from $t$ to $T$.

        	The integral $I_{1,b}$ is treated in a similar manner. We once again swap the order of integration between $z$ and $w$. Then Lemma~\ref{lem:1} will be used since $z_{2\lambda}$ is actually a logarithmic function. To utilize Lemma~\ref{lem:1}, we need to set
        		$$
        			a_1 = \fr{1}{\sqrt{n\sigma_Y^2}}, \enskip b_1 = \fr{n\mu_Y}{\sqrt{n\sigma_Y^2}}, \enskip
        			a_2 = \fr{1}{\sigma\sqrt{u-t}}, \enskip b_2 = z_{2\lambda}\left( \fr{x}{z}, t, u\right),
        		$$
	and integrating with respect to $w$ leaves us with
			\begin{align*}
				I_{1,b} &= rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}  e^{(r+\lambda)(u-t)} \int_{S^*(u)}^\infty \fr{1}{z}  N\left(Z_n \left( \fr{x}{z},t,u  \right) \right) \,\d z \, \d u,
			\end{align*}
	with $Z_n$ defined in~\eqref{eqn:zn}. We once again incorporate Lemma~\ref{lem:2a} to complete the integral in $z$ by setting 
		$$
			a = S^*(u), \enskip b = \infty, \enskip a_1 = \fr{1}{\sqrt{n\sigma_Y^2 + \sigma^2(u-t)}}, \enskip
			b_1 = Z_n\left( \fr{x}{z}, t, u \right),
		$$
		to obtain
		$$
			I_{1,b} = rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!}  e^{(r+\lambda)(u-t)} N\left(Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u.
		$$
		Now that all the simplifications have been performed, we now recover $I_1$ by adding $I_{1,a}$ and $I_{1,b}$ to get
		\begin{align}
			I_1 &= rK\int_t^T e^{(r+\lambda)(u-t)}N\left(z_{2\lambda}\left( \fr{x}{S^*(u)},t,u\right) \right) \, \d u \nonumber \\
			 &\quad rK  \int_t^T  \ds\sum\limits_{n=1}^{\infty} \fr{(\lambda(u-t))^n}{n!}  e^{(r+\lambda)(u-t)} N\left(Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u \nonumber \\
			 &= rK \ds\sum\limits_{n=0}^{\infty}\int_t^T  \fr{(\lambda(u-t))^n}{n!} e^{(r+\lambda)(u-t)} N\left(Z_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u, \label{eqn:I1call}
		\end{align}
		where the summation can be extended to $n=0$ when we see that $z_{2\lambda} = Z_n$ for $n=0$. Like the American put, we could not immediately make this observation since $\J$ had a fraction where $n=0$ would render it undefined.

		The integral $I_2$ follows a similar path for the lemmas and techniques used in deriving the analogous term with the American put. The lengthy calculations will be omitted, but the result is
        	\begin{equation}
        		\label{eqn:I2put}
        		I_2 = qx  \ds\sum\limits_{n=0}^{\infty}\int_t^T   \fr{(\lambda(u-t))^n}{n!} e^{n\mu_Y + n\sigma_Y^2/2} e^{(q+\lambda + \kappa\lambda)(u-t)} N\left( D_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u,
        	\end{equation}
	with $D_n$ defined in~\eqref{eqn:Dn}. 
	However, we will be providing the complete derivation and solution of $I_3$ as this term is rather complicated. As we will see, the result of $I_3$ will be a double integral which is more ideal to work with in comparison to a quadruple integral.
